Energy and the CES production function

### 2015-09-10 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Now using better digits in tables.

myXTable(data_CES_SR_gof,
         caption="Scale parameter~($\\theta$), Solow residual~($\\lambda$), and sum of squared errors~($sse$) for all modeling choices.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=4)
@

@@

<<CES_alpha, results="asis">>=
data_CES_alpha <- 
  table_data %>% 
  filter(Model=="CES" | Model=="Ref.") %>% 
  select(Country, Model, CSP, flavor, Energy, Nest, alpha_1, alpha_2, alpha_3) %>%
  plyr::rename(c("flavor" = "Factors of prod.",
                 "alpha_1" = "$\\alpha_k$",
                 "alpha_2" = "$\\alpha_l$",
                 "alpha_3" = "$\\alpha_e$"))
myXTable(data_CES_alpha,
         caption="Output elasticities~($\\alpha$) for all models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=2)
@

@@

<<CES_sigma_nest_aware_inner, results="asis">>=
sigma_inner_data <- 
  table_data %>% 
  filter(Model=="CES") %>% 
  select(Country, CSP, flavor, Energy, Nest, sigma_12, sigma_23, sigma_13) %>%
  plyr::rename( c("flavor" = "Factors of prod.",
                  "sigma_12" = "$\\sigma_{kl}$",
                  "sigma_23" = "$\\sigma_{le}$",
                  "sigma_13" = "$\\sigma_{ek}$"))
#
myXTable(sigma_inner_data,
         caption="Elasticities of substitution~($\\sigma$) for inner nests of CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=2)
@

@@

<<CES_sigma_nest_aware_outer, results="asis">>=
sigma_outer_data <- 
  table_data %>% 
  filter(Model=="CES") %>% 
  select(Country, CSP, flavor, Energy, Nest, sigma_12_3, sigma_23_1, sigma_13_2) %>%
  plyr::rename(c("flavor" = "Factors of prod.", 
                 "sigma_12_3" = "$\\sigma_{(kl)e}$",
                 "sigma_23_1" = "$\\sigma_{(le)k}$",
                 "sigma_13_2" = "$\\sigma_{(ek)l}$"))
myXTable(sigma_outer_data,
         caption="Elasticities of substitution~($\\sigma$) for outer nests of CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=2)
@

>>>>

myXTable(data_CES_SR_gof,
         caption="Scale parameter~($\\theta$), Solow residual~($\\lambda$), and sum of squared errors~($sse$) for all modeling choices.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=c(1,1,1,1,1,1,1, 2, 4, 3))
@

@@

<<CES_alpha, results="asis">>=
data_CES_alpha <- 
  table_data %>% 
  filter(Model=="CES" | Model=="Ref.") %>% 
  select(Country, Model, CSP, flavor, Energy, Nest, alpha_1, alpha_2, alpha_3) %>%
  plyr::rename(c("flavor" = "Factors of prod.",
                 "alpha_1" = "$\\alpha_k$",
                 "alpha_2" = "$\\alpha_l$",
                 "alpha_3" = "$\\alpha_e$"))
myXTable(data_CES_alpha,
         caption="Output elasticities~($\\alpha$) for all models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=3)
@

@@

<<CES_sigma_nest_aware_inner, results="asis">>=
sigma_inner_data <- 
  table_data %>% 
  filter(Model=="CES") %>% 
  select(Country, CSP, flavor, Energy, Nest, sigma_12, sigma_23, sigma_13) %>%
  plyr::rename( c("flavor" = "Factors of prod.",
                  "sigma_12" = "$\\sigma_{kl}$",
                  "sigma_23" = "$\\sigma_{le}$",
                  "sigma_13" = "$\\sigma_{ek}$"))
#
myXTable(sigma_inner_data,
         caption="Elasticities of substitution~($\\sigma$) for inner nests of CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=c(1,1,1,1,1,1, 3,3,3))
@

@@

<<CES_sigma_nest_aware_outer, results="asis">>=
sigma_outer_data <- 
  table_data %>% 
  filter(Model=="CES") %>% 
  select(Country, CSP, flavor, Energy, Nest, sigma_12_3, sigma_23_1, sigma_13_2) %>%
  plyr::rename(c("flavor" = "Factors of prod.", 
                 "sigma_12_3" = "$\\sigma_{(kl)e}$",
                 "sigma_23_1" = "$\\sigma_{(le)k}$",
                 "sigma_13_2" = "$\\sigma_{(ek)l}$"))
myXTable(sigma_outer_data,
         caption="Elasticities of substitution~($\\sigma$) for outer nests of CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=c(1,1,1,1,1,1, 3,3,3))
@
